Hydras \& Co.

### 2022-05-16 doc/hydra-chapter.tex
revision book (chap 2, done)

Both theorems are proved with the help of the  following strongly specified function:

@@

@@

When one wants to prove a termination theorem with the help of a variant, 
one has to consider first a well-founded set $(A,<)$, then a strictly decreasing measure on this set.  The following two lemmas show that if  the order structure $(A,<)$ is too simple, it is useless to look for a convenient measure, which simply no exists. Such kind of result is useful, because it saves you time and effort.

@@

Let us assume there exists some variant $m$ from \texttt{Hydra} into \texttt{nat} for proving
    the  termination of all hydra battles.

>>>>

@@

\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Theorems}{Hydra.Hydra\_Theorems}}

@@

When one wants to prove a termination theorem with the help of a variant, 
one has to consider first a well-founded set $(A,<)$, then a strictly decreasing measure on this set.  The following  lemma shows that,  if  the order structure $(A,<)$ is too simple, it is useless to look for a convenient measure, which simply no exists. Such kind of result is useful, because it saves you time and effort.

@@

Let us assume there exists some variant $m$ from \texttt{Hydra} into (\texttt{nat},$<$)  for proving
    the  termination of all hydra battles.
